Untitled

### 2020-12-09 Manuscript/Manuscript_Paper.Rmd
Update Manuscript_Paper.Rmd

@@

Even though genetic distance estimation in MEGAX did not offer all of the models and parameters as suggested by model testing, all of the models and parameters were available for phylogentic tree analysis and genetic distance can be exported from these trees. However, this has to be done manually by opening the tree file in MEGAX and exporting the distance matrix as either an Excel or CSV file and is therefore not feasible when hundreds or thousands of genetic distance matrices are needed.

@@

The genes showing greatest identity (lowest distance) to P. septica are distributed across the genome for both M. calida and M. gaviniae (Figures 1 and 2), further suggesting Mixta and Pantoea species have a recent common ancestor. If many genes were horizontally transferred in a single event, then large blocks of genes from a single species would be expected. However, the Erwinia lines (green) are fairly even throughout the genome and the outgroup lines (red and orange) are separated with genes in between. This suggests that Mixta underwent many HGT after speciation from Pantoea.

Positional effects of all of the species and range of the distances were also evaluated (Figures 3 and 4). For most genes, the genetic distance for each of the eight species ranged from 0 to 1.5 with only a few greater than 2. The cluster of genes around ID 425 in both M. calida and M. gaviniae have a very small range and so are highly conserved among all of the species. These genes were annotated as being ribosomal genes. Furthermore, Pantoea species (blue dots) are typically the closest relative to Mixta, followed by Erwinia (green). The Tatumella species (purple and pink) and the outgroup species (red and orange) vary as to which are the furthest relative to Mixta.

@@

@@

>>>>

## Nucleotide and Amino Acid Identity
Individual species sequences of genes were aligned to both of the corresponding *Mixta* sequences in turn. Alignments were done in `R` using the same methods as for gene alignment of the whole gene file. The aligned sequences were then split into the individual sites using the `str_split()` function (package: stringr) [@]. Using base `R` code, a function was created to calculate the number of identical sites between the two sequences over the total number of sites to give a percentage of similar identity. Values that equal or are close to 100% are more similar to the *Mixta* sequences.

@@

Even though genetic distance estimation in MEGAX did not offer all of the models and parameters as suggested by model testing, all of the models and parameters were available for phylogenetic tree analysis and genetic distance can be exported from these trees. However, this has to be done manually by opening the tree file in MEGAX and exporting the distance matrix as either an Excel or CSV file and is therefore not feasible when hundreds or thousands of genetic distance matrices are needed.

@@

For the nucleotide sequences, there were no discernible patterns in closest relatives to *M. calida* genes with the exception of the seven genes that are most closely related to a *Tatumella* species (pink) which are only in the first half of the *M. calida* genome (Figure 3). Genes that are most closely related to *Pantoea* species (blue) were distributed throughout the genome (Figure 3), which further suggests that *Mixta* and *Pantoea* have a recent ancestor. Unexpectedly, genes that are most closely related to other genera, particularly to *E. cloacae* (orange) are also distributed throughout the genome (Figure 3).

@@

Less genes are closely related to *P. septica* when analyzing the amino acid sequences of the *M. calida* genes and more are closely related to *P. agglomerans*, the *Erwinia* species, the *Tatumella* species, and *E. cloacae* (Figure 4). Nevertheless, no obvious patterns arose in closest relatives to the *Mixta* genes (Figure 4). The *Mixta* genes that have changed their allegiance between the nucleotide and amino acid analyses may be a result of redundancy of the genetic code.

@@

If many genes were horizontally transferred in a single event, then large blocks of genes from a single species would be expected. However, this is not the case for any of species. There are several hypotheses as to why. One is that it is possible that the *Mixta* genome underwent many HGT events after speciation from *Pantoea*; however, further research into the origins of these genes and the frequency of HGT events with *Mixta* and other genera within the *Erwiniaceae* is needed. Another hypothesis is that the gene sequence is so well-conserved that the genetic distance between *Mixta* and more than one of the other species are near identical. Since only one species was extracted for the closest relative to each *Mixta* gene, it is possible that a species was called at random if there was tie between more than one species for having the shortest distance to *Mixta*. For example, if the genetic distance from *M. calida* to both *P. septica* and *E. amylovora* for a single gene was 0.012 and this was the shortest distance for that gene, then both species are tied for closest relative for that gene. However, since only one can be determined as closest relative, then closest relative may have been decided by the computer program based on another characteristic such as alphabetical order. Therefore, quantitative analysis or computing a phylogenetic tree to view the two-dimensional results is needed.

## Nucleotide and Amino Acid Identity
### Nucleotide Identity

### Amino Acid Identity

## A Comparison Between Evolutionary Change and Site Identity

## Phylogenetic Trees
